Analysing Constraint Grammars with a SAT-solver

### 2016-02-26 paper/lrec/eval_futurework.tex
better explanatio of DetPos(Not)Zijn example

\begin{itemize}
\item[] 
\begin{verbatim}SELECT DetPos IF (-1 Verb) (0 "zijn") 
                 ( 1 Noun) ;
SELECT DetPosNotZijn IF (1 Noun) ;
\end{verbatim}
\end{itemize}

On the first glance it seems that there is no conflict: the first rule requires a Det Pos which is at the same time ``zijn'', as seen by the requirement \texttt{(0 "zijn")}. However, this has a different semantics in VISL CG-3, which is also repeated in our tool. The rules match a situation where there is \emph{any} Det Pos and \emph{any} zijn, including the verb. The correct way to formulate the first rule would be the following:

\begin{itemize}
\item[] \texttt{SELECT DetPos + "zijn" IF (-1 Verb) (1 Noun) ;}
\end{itemize}

>>>>

\begin{itemize}
\item[] 
\begin{verbatim}
SELECT DetPosNotZijn IF (1 Noun) ;
SELECT DetPos IF (-1 (vbser pres p3 sg)) 
                 (0 "zijn") (1 Noun);
\end{verbatim}
\end{itemize}

The condition of the second rule cannot be true: there can never be a ``zijn'' in the target, because the previous rule has selected everything that is a possessive determiner and not ``zijn''. 
%Not firing is not an option: if conditions of the first rule do not hold, then they will not hold for the second either. If the target is the only left, then 
% "target" in case of SELECT means complement of the mentioned target. so 
%    some of [adj, det pos zijn, verb zijn, punct, ...]  is true
%    all of  [det pos f sg, det pos m pl, det pos foo bar] are false.
% ie. there has been a rule that has removed detPosNotZijn, or they haven't been there in the first place.
%

Another remark on this formulation of a rule. 
As per VISL CG-3, the condition \texttt{(0 "zijn")} does not require that the input would have determiner and ``zijn'' in the same reading: just that there is any determiner and any ``zijn'' in the cohort. 
The first example of a rule conflict had a similar requirement, but used correctly: the intended semantics was indeed that the adjective and the adverb are in different readings. However, in this case, the correct way to express the target is \texttt{SELECT DetPos + "zijn"}.

Can we catch this additional problem with our tool? The example word constructed by the SAT-solver may as likely be one of the following:

\begin{itemize}
\item[a.] \begin{verbatim}
"w2"
    w2<det><pos><f><sg>
    w2<vbser><inf><"zijn">
\end{verbatim}

\item[b.] \begin{verbatim}
"w2"
    w2<det><pos><mfn><pl><"zijn">
\end{verbatim}
\end{itemize}

In the latter case, the grammar writer would hopefully notice the imprecise definition and change their definition. However, this is more of a happy side effect than intended feature---the grammar writer cannot count on our tool to notice all similar cases.
We could add a feature that alerts in all cases where a condition with 0 is used, or even automatically construct a version of the rule that moves whatever tags in the 0-condition into the target.
